\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{datetime}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in} % taller text area to reduce bottom gap

\raggedbottom
\raggedright
\setlength{\parskip}{1.4em} % space between paragraphs
\setlength{\parindent}{0pt} % no paragraph indentation
\linespread{1.15} % line spacing

% Sections formatting
\titleformat{\section}{
    \vspace{3pt}\scshape\raggedright\Large\color{MidnightBlue}
}{}{0em}{}[\vspace{3pt}\color{MidnightBlue}\titlerule\vspace{6pt}]

%-------------------------
% Custom commands
\newcommand{\letterHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large #1} & #5 \\  % Right side is date
    #2 & \\
    #3 & \\
    #4 & \\
    \end{tabular*}
    \vspace{15pt}
}

\newcommand{\letterRecipient}[3]{
    \textbf{\large To:} #1 \\
    \textbf{\large Position:} #2 \\
    \textbf{\large Company:} #3 \\
    \vspace{12pt}
}

\newcommand{\letterSubject}[1]{
    \textbf{\large Subject:} #1 \\
    \vspace{15pt}
}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%

\begin{document}

%----------HEADING----------
    \letterHeading
    {Mahdi Jellali}
    {Sousse, Tunisia}
    {+216 55 402 817 \\ \href{mailto:mahdijellali2001@gmail.com}{mahdijellali2001@gmail.com}}
    {\href{https://github.com/mahdiJ2001}{github.com/mahdiJ2001} $|$ \href{https://concise-code-display.vercel.app/}{concise-code-display.vercel.app} $|$ \href{https://www.linkedin.com/in/mahdi-jellali/}{linkedin.com/in/mahdi-jellali}}
    {\today}

%-----------RECIPIENT-----------
    \letterRecipient
    {Hiring Manager}
    {AI Software Engineer}
    {Synaptech Labs, 123 Innovation Drive, Silicon Valley, CA}

%-----------SUBJECT-----------
    \letterSubject{Application for AI Software Engineer Position}

%-----------BODY-----------
    Dear Hiring Manager,

    I am thrilled to apply for the AI Software Engineer role at Synaptech Labs, where I can leverage my passion for machine learning and data-driven intelligence to build cutting-edge systems. With a strong foundation in deep learning frameworks, including TensorFlow, and a proficiency in Python, I am confident in my ability to design, train, and deploy production-ready AI models that solve complex business problems at scale.

    Throughout my experiences, I have developed a knack for collaborating with cross-functional teams to translate research into deployable solutions. My projects, such as the AI Resume Analyzer and Medical Image Classifier, demonstrate my ability to apply machine learning concepts to real-world problems. I am particularly excited about the opportunity to work alongside data scientists, cloud engineers, and backend developers to drive innovation and growth at Synaptech Labs.

    I am impressed by Synaptech Labs' commitment to pushing the boundaries of AI and its applications. I am eager to contribute my skills and experience to help advance the company's mission and goals. With a strong understanding of data preprocessing, feature engineering, and model evaluation, I am well-equipped to monitor model performance, implement retraining workflows, and ensure reliability in production. I am also familiar with cloud platforms, including AWS, and containerization tools, such as Docker, which I believe are essential for the success of this role.

    Thank you for considering my application. I would be delighted to discuss in greater detail how my dedication, enthusiasm, and personal qualities align with your needs, and how I can contribute meaningfully to your team. I look forward to the possibility of joining Synaptech Labs and helping drive its mission forward with commitment, passion, and integrity.

    Sincerely,\\[12pt]

    Mahdi Jellali

\end{document}