\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{datetime}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in} % taller text area to reduce bottom gap

\raggedbottom
\raggedright
\setlength{\parskip}{1.4em} % space between paragraphs
\setlength{\parindent}{0pt} % no paragraph indentation
\linespread{1.15} % line spacing

% Sections formatting
\titleformat{\section}{
    \vspace{3pt}\scshape\raggedright\Large\color{MidnightBlue}
}{}{0em}{}[\vspace{3pt}\color{MidnightBlue}\titlerule\vspace{6pt}]

%-------------------------
% Custom commands
\newcommand{\letterHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large #1} & #5 \\  % Right side is date
    #2 & \\
    #3 & \\
    #4 & \\
    \end{tabular*}
    \vspace{15pt}
}

\newcommand{\letterRecipient}[3]{
    \textbf{\large To:} #1 \\
    \textbf{\large Position:} #2 \\
    \textbf{\large Company:} #3 \\
    \vspace{12pt}
}

\newcommand{\letterSubject}[1]{
    \textbf{\large Subject:} #1 \\
    \vspace{15pt}
}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%

\begin{document}

%----------HEADING----------
    \letterHeading
    {Mahdi Jellali}
    {Sousse, Tunisia}
    {+216 55 402 817 \\ \href{mailto:mahdijellali2001@gmail.com}{mahdijellali2001@gmail.com}}
    {\href{https://github.com/mahdiJ2001}{github.com/mahdiJ2001} $|$ \href{https://concise-code-display.vercel.app/}{concise-code-display.vercel.app} $|$ \href{https://www.linkedin.com/in/mahdi-jellali/}{linkedin.com/in/mahdi-jellali}}
    {\today}

%-----------RECIPIENT-----------
    \letterRecipient
    {Hiring Manager}
    {Full-Stack Software Engineer}
    {SkyBridge Solutions, 123 Innovation Drive, Silicon Valley, CA}

%-----------SUBJECT-----------
    \letterSubject{Application for Full-Stack Software Engineer Position}

%-----------BODY-----------
    Dear Hiring Manager,

    I am thrilled to apply for the Full-Stack Software Engineer position at SkyBridge Solutions, where I can leverage my passion for building next-generation web applications to connect thousands of users daily. With a strong background in backend engineering, distributed systems, and applied mathematics, I am confident that I would be an excellent fit for your team. I am particularly drawn to SkyBridge's values of innovation, collaboration, and craftsmanship, which align with my own principles of delivering high-quality software solutions.

    Throughout my experiences, I have had the opportunity to work on various projects that demonstrate my skills in developing responsive and user-friendly web interfaces using React and Angular, as well as designing and implementing scalable backend services using Node.js, Express, and Spring Boot. For instance, in my role as a Backend Developer Intern at Wevioo, I contributed to a microservices-based patient management system using Spring Boot, Kafka, and gRPC, where I improved backend performance by implementing asynchronous event handling and optimizing serialization. I am excited about the prospect of bringing my expertise to SkyBridge and contributing to the design and development of impactful features that ship quickly and efficiently.

    I am a strong believer in the importance of collaboration, problem-solving, and communication in software development. My experience working with cross-functional teams, including designers, engineers, and product leads, has taught me the value of active listening, clear documentation, and respectful feedback. I am eager to join a team that shares my passion for building software that is simple, reliable, and delightful to use. I am confident that my skills, experience, and enthusiasm make me an ideal candidate for this role, and I look forward to the opportunity to discuss my application and how I can contribute to SkyBridge's mission.

    Thank you for considering my application. I would be delighted to discuss in greater detail how my skills and experience align with the requirements of the Full-Stack Software Engineer position and how I can contribute to the success of SkyBridge Solutions.

    Sincerely,\\[12pt]

    Mahdi Jellali

\end{document}