\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{datetime}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in} % taller text area to reduce bottom gap

\raggedbottom
\raggedright
\setlength{\parskip}{1.4em} % space between paragraphs
\setlength{\parindent}{0pt} % no paragraph indentation
\linespread{1.15} % line spacing

% Sections formatting
\titleformat{\section}{
    \vspace{3pt}\scshape\raggedright\Large\color{MidnightBlue}
}{}{0em}{}[\vspace{3pt}\color{MidnightBlue}\titlerule\vspace{6pt}]

%-------------------------
% Custom commands
\newcommand{\letterHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large #1} & #5 \\  % Right side is date
    #2 & \\
    #3 & \\
    #4 & \\
    \end{tabular*}
    \vspace{15pt}
}

\newcommand{\letterRecipient}[3]{
    \textbf{\large To:} #1 \\
    \textbf{\large Position:} #2 \\
    \textbf{\large Company:} #3 \\
    \vspace{12pt}
}

\newcommand{\letterSubject}[1]{
    \textbf{\large Subject:} #1 \\
    \vspace{15pt}
}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%

\begin{document}

%----------HEADING----------
    \letterHeading
    {Mahdi Jellali}
    {Sousse, Tunisia}
    {+216 55 402 817 \\ \href{mailto:mahdijellali2001@gmail.com}{mahdijellali2001@gmail.com}}
    {\href{https://github.com/mahdiJ2001}{github.com/mahdiJ2001} $|$ \href{https://concise-code-display.vercel.app/}{concise-code-display.vercel.app} $|$ \href{https://www.linkedin.com/in/mahdi-jellali/}{linkedin.com/in/mahdi-jellali}}
    {\today}

%-----------RECIPIENT-----------
    \letterRecipient
    {Hiring Manager}
    {Software Engineer}
    {TechNova Labs, 123 Tech Drive, Silicon Valley, CA}

%-----------SUBJECT-----------
    \letterSubject{Application for Software Engineer Position}

%-----------BODY-----------
    Dear Hiring Manager,

    I am thrilled to apply for the Software Engineer position at TechNova Labs, where I can leverage my passion for designing and implementing scalable microservices to contribute to the success of your backend development team. With a strong foundation in distributed systems, Java, and Spring Boot, I am confident that my skills and experience make me an ideal fit for this role. My previous experience as a Backend Developer Intern at Wevioo, where I contributed to a microservices-based patient management system using Spring Boot, Kafka, and gRPC, has given me a deep understanding of the importance of efficient and maintainable code.

    Throughout my academic and professional journey, I have developed a strong ability to work collaboratively with cross-functional teams to deliver end-to-end solutions. My experience with RESTful APIs, cloud environments, and containerization using Docker has equipped me with the skills to develop and maintain scalable backend services. I am particularly excited about the opportunity to work with TechNova Labs' team to design, implement, and maintain scalable microservices using Java and Spring Boot.

    I am impressed by TechNova Labs' commitment to innovation and customer satisfaction, and I am eager to be a part of a team that values collaboration, dedication, and continuous growth. My certifications in AWS Cloud Practitioner, Oracle Java Programmer, and TensorFlow Developer, along with my experience in CI/CD pipelines, have prepared me to make a significant contribution to your team. I am confident that my passion for software engineering, combined with my technical skills and experience, make me an excellent fit for this role.

    Thank you for considering my application. I would be delighted to discuss in greater detail how my skills and experience align with your needs and how I can contribute to the success of TechNova Labs. I look forward to the opportunity to join your team and contribute to the company's mission.

    Sincerely,\\[12pt]

    Mahdi Jellali

\end{document}