\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{datetime}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in} % taller text area to reduce bottom gap

\raggedbottom
\raggedright
\setlength{\parskip}{1.4em} % space between paragraphs
\setlength{\parindent}{0pt} % no paragraph indentation
\linespread{1.15} % line spacing

% Sections formatting
\titleformat{\section}{
    \vspace{3pt}\scshape\raggedright\Large\color{MidnightBlue}
}{}{0em}{}[\vspace{3pt}\color{MidnightBlue}\titlerule\vspace{6pt}]

%-------------------------
% Custom commands
\newcommand{\letterHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large #1} & #5 \\  % Right side is date
    #2 & \\
    #3 & \\
    #4 & \\
    \end{tabular*}
    \vspace{15pt}
}

\newcommand{\letterRecipient}[3]{
    \textbf{\large To:} #1 \\
    \textbf{\large Position:} #2 \\
    \textbf{\large Company:} #3 \\
    \vspace{12pt}
}

\newcommand{\letterSubject}[1]{
    \textbf{\large Subject:} #1 \\
    \vspace{15pt}
}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%

\begin{document}

%----------HEADING----------
    \letterHeading
    {Ahmed Aziz Daoud}
    {Chicago, IL, USA}
    {+1 234 556 786 \\ \href{mailto:xewihap310@hh7f.com}{xewihap310@hh7f.com}}
    {\href{https://github.com/DaoudAA}{github.com/DaoudAA}}
    {\today}

%-----------RECIPIENT-----------
    \letterRecipient
    {Hiring Manager}
    {Regional Sales Executive}
    {Apple, 1 Infinite Loop, Cupertino, CA}

%-----------SUBJECT-----------
    \letterSubject{Application for Regional Sales Executive Position}

%-----------BODY-----------
    Dear Hiring Manager,

    I am thrilled to apply for the Regional Sales Executive role at Apple, where I can leverage my passion for driving sales growth, building strong client relationships, and navigating fast-paced environments. With a proven track record of exceeding sales targets and a deep understanding of the sales landscape, I am confident that my skills and experience make me an ideal fit for this position.

    Throughout my career, I have consistently demonstrated my ability to manage a portfolio of regional clients, identify new business opportunities, and collaborate with internal teams to ensure client success. My experience as a Senior Sales Executive at Horizon Tech Solutions, where I increased annual revenue by 35% through strategic client acquisition and upselling existing accounts, has prepared me to tackle the challenges of this role. I am also proficient in CRM software, including Salesforce, HubSpot, and Zoho CRM, which I believe will be a valuable asset in this position.

    I am particularly drawn to Apple's commitment to innovation and customer satisfaction. As a sales professional, I thrive in environments where I can build long-term relationships with key decision-makers, conduct product presentations and demos tailored to client needs, and collaborate with marketing and customer success teams to implement campaigns and promotions. My experience in account management, client retention, and prospecting has equipped me with the skills to drive sales growth and ensure client success.

    I am excited about the opportunity to join Apple's team and contribute my skills and experience to help drive sales growth and achieve business objectives. Thank you for considering my application. I would be delighted to discuss in greater detail how my dedication, enthusiasm, and personal qualities align with your needs, and how I can contribute meaningfully to your team.

    Sincerely,\\[12pt]

    Ahmed Aziz Daoud

\end{document}