\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{datetime}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in} % taller text area to reduce bottom gap

\raggedbottom
\raggedright
\setlength{\parskip}{1.4em} % space between paragraphs
\setlength{\parindent}{0pt} % no paragraph indentation
\linespread{1.15} % line spacing

% Sections formatting
\titleformat{\section}{
    \vspace{3pt}\scshape\raggedright\Large\color{MidnightBlue}
}{}{0em}{}[\vspace{3pt}\color{MidnightBlue}\titlerule\vspace{6pt}]

%-------------------------
% Custom commands
\newcommand{\letterHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large #1} & #5 \\  % Right side is date
    #2 & \\
    #3 & \\
    #4 & \\
    \end{tabular*}
    \vspace{15pt}
}

\newcommand{\letterRecipient}[3]{
    \textbf{\large To:} #1 \\
    \textbf{\large Position:} #2 \\
    \textbf{\large Company:} #3 \\
    \vspace{12pt}
}

\newcommand{\letterSubject}[1]{
    \textbf{\large Subject:} #1 \\
    \vspace{15pt}
}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%

\begin{document}

%----------HEADING----------
    \letterHeading
    {Karim Haddad}
    {Stuttgart, Germany}
    {+21655903247 \\ \href{mailto:mehdi.jellali@etudiant-enit.utm.tn}{mehdi.jellali@etudiant-enit.utm.tn}}
    {\href{https://github.com/karimhaddad}{github.com/karimhaddad} $|$ \href{https://www.linkedin.com/in/karimhaddad}{linkedin.com/in/karimhaddad}}
    {\today}

%-----------RECIPIENT-----------
    \letterRecipient
    {Hiring Manager}
    {Junior Embedded Software Engineer (IoT & C++)}
    {Bosch Connected Devices, Stuttgart, Germany}

%-----------SUBJECT-----------
    \letterSubject{Application for Junior Embedded Software Engineer (IoT & C++) Position}

%-----------BODY-----------
    Dear Hiring Manager,

    I am thrilled to apply for the Junior Embedded Software Engineer (IoT & C++) role at Bosch Connected Devices, where I can leverage my passion for IoT and C++ to contribute to the development of innovative smart home solutions. With a strong foundation in software engineering and a keen interest in embedded systems, I am confident that I would thrive in your dynamic team.

    Throughout my academic and professional journey, I have gained hands-on experience with C++ and embedded programming, particularly in the context of IoT projects. Notably, my work on the Smart Parking System and Home Energy Monitor projects has equipped me with a solid understanding of developing and optimizing embedded C++ code for microcontrollers, as well as implementing communication protocols such as MQTT. I am excited about the prospect of applying these skills to contribute to the next generation of connected systems at Bosch Connected Devices.

    As a collaborative and adaptable individual, I am drawn to Bosch Connected Devices' commitment to innovation and teamwork. My experience in machine learning, cloud deployment, and full-stack development has taught me the value of interdisciplinary collaboration and the importance of staying up-to-date with emerging technologies. I am eager to work closely with hardware engineers to integrate sensors and actuators, and to write unit tests and perform debugging using tools like JTAG and GDB.

    I am particularly impressed by Bosch Connected Devices' mission to create cutting-edge IoT solutions that enhance people's lives. I am confident that my strong work ethic, passion for learning, and commitment to excellence would make me a valuable asset to your team. I look forward to the opportunity to discuss my application and how I can contribute to the success of Bosch Connected Devices.

    Thank you for considering my application. I am excited about the prospect of joining your team and contributing to the development of innovative IoT solutions.

    Sincerely,\\[12pt]

    Karim Haddad

\end{document}