\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{datetime}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in} % taller text area to reduce bottom gap

\raggedbottom
\raggedright
\setlength{\parskip}{1.4em} % space between paragraphs
\setlength{\parindent}{0pt} % no paragraph indentation
\linespread{1.15} % line spacing

% Sections formatting
\titleformat{\section}{
    \vspace{3pt}\scshape\raggedright\Large\color{MidnightBlue}
}{}{0em}{}[\vspace{3pt}\color{MidnightBlue}\titlerule\vspace{6pt}]

%-------------------------
% Custom commands
\newcommand{\letterHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large #1} & #5 \\  % Right side is date
    #2 & \\
    #3 & \\
    #4 & \\
    \end{tabular*}
    \vspace{15pt}
}

\newcommand{\letterRecipient}[3]{
    \textbf{\large To:} #1 \\
    \textbf{\large Position:} #2 \\
    \textbf{\large Company:} #3 \\
    \vspace{12pt}
}

\newcommand{\letterSubject}[1]{
    \textbf{\large Subject:} #1 \\
    \vspace{15pt}
}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%

\begin{document}

%----------HEADING----------
    \letterHeading
    {Karim Haddad}
    {Tunis, Tunisia}
    {+216 559 032 47 \\ \href{mailto:mehdi.jellali@etudiant-enit.utm.tn}{mehdi.jellali@etudiant-enit.utm.tn}}
    {\href{https://github.com/karimhaddad}{github.com/karimhaddad} $|$ \href{https://www.linkedin.com/in/karimhaddad}{linkedin.com/in/karimhaddad}}
    {October 19, 2025}

%-----------RECIPIENT-----------
    \letterRecipient
    {Hiring Manager}
    {Junior Embedded Software Engineer}
    {Bosch Connected Devices, Stuttgart, Germany}

%-----------SUBJECT-----------
    \letterSubject{Application for Junior Embedded Software Engineer (IoT & C++) Position}

%-----------BODY-----------
    Dear Hiring Manager,

    I am writing to express my strong enthusiasm for the Junior Embedded Software Engineer (IoT & C++) position at Bosch Connected Devices. With a solid foundation in C/C++ and embedded programming, I am confident that my skills and passion for IoT development make me an ideal candidate for this role. I am particularly drawn to Bosch's commitment to innovation and excellence in the field of connected devices, and I am excited about the opportunity to contribute to the development of the next generation of smart home systems.

    Throughout my academic and professional journey, I have gained hands-on experience in developing embedded C++ code for microcontrollers, implementing communication protocols such as MQTT and BLE, and collaborating with hardware engineers to integrate sensors and actuators. My experience with IoT platforms, including ESP32 and Raspberry Pi, has equipped me with the knowledge and skills necessary to design and develop innovative IoT-based solutions. I am also familiar with debugging tools like JTAG and GDB, which will enable me to efficiently troubleshoot and optimize my code.

    In addition to my technical skills, I possess a strong sense of teamwork, problem-solving, and adaptability, which I believe are essential for success in this role. My experience in working on various projects, including the development of an IoT-based parking system and a home energy monitor, has taught me the importance of collaboration, creativity, and attention to detail. I am excited about the opportunity to bring my skills and experience to Bosch Connected Devices and contribute to the development of innovative solutions that make a meaningful impact.

    Thank you for considering my application. I would be delighted to discuss in greater detail how my skills and experience align with the requirements of this role and how I can contribute to the success of Bosch Connected Devices. I look forward to the possibility of joining your team and being a part of the company's mission to shape the future of connected devices.

    Sincerely,\\[12pt]

    Karim Haddad

\end{document}