\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{datetime}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in} % taller text area to reduce bottom gap

\raggedbottom
\raggedright
\setlength{\parskip}{1.4em} % space between paragraphs
\setlength{\parindent}{0pt} % no paragraph indentation
\linespread{1.15} % line spacing

% Sections formatting
\titleformat{\section}{
    \vspace{3pt}\scshape\raggedright\Large\color{MidnightBlue}
}{}{0em}{}[\vspace{3pt}\color{MidnightBlue}\titlerule\vspace{6pt}]

%-------------------------
% Custom commands
\newcommand{\letterHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large #1} & #5 \\  % Right side is date
    #2 & \\
    #3 & \\
    #4 & \\
    \end{tabular*}
    \vspace{15pt}
}

\newcommand{\letterRecipient}[3]{
    \textbf{\large To:} #1 \\
    \textbf{\large Position:} #2 \\
    \textbf{\large Company:} #3 \\
    \vspace{12pt}
}

\newcommand{\letterSubject}[1]{
    \textbf{\large Subject:} #1 \\
    \vspace{15pt}
}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%

\begin{document}

%----------HEADING----------
    \letterHeading
    {Mahdi Jellali}
    {Sousse, Tunisia}
    {+216 55 402 817 \\ \href{mailto:mahdijellali2001@gmail.com}{mahdijellali2001@gmail.com}}
    {\href{https://github.com/mahdiJ2001}{github.com/mahdiJ2001} $|$ \href{https://concise-code-display.vercel.app/}{concise-code-display.vercel.app} $|$ \href{https://www.linkedin.com/in/mahdi-jellali/}{linkedin.com/in/mahdi-jellali}}
    {\today}

%-----------RECIPIENT-----------
    \letterRecipient
    {Hiring Manager}
    {Machine Learning Engineer}
    {NeuroGrid Technologies, 123 Innovation Drive, Silicon Valley, CA}

%-----------SUBJECT-----------
    \letterSubject{Application for Machine Learning Engineer Position}

%-----------BODY-----------
    Dear Hiring Manager,

    I am thrilled to apply for the Machine Learning Engineer role at NeuroGrid Technologies, where I can leverage my passion for building high-quality software systems and contributing to innovative projects. With a strong foundation in computer science and software engineering, I am confident that my skills and experience make me an ideal fit for this position. I am particularly drawn to NeuroGrid's commitment to collaboration, continuous growth, and pushing the boundaries of what is possible with machine learning.

    Throughout my academic and professional journey, I have developed a solid understanding of algorithms, data structures, and software design principles. My experience as a Backend Developer Intern at Wevioo, where I contributed to a microservices-based patient management system using Spring Boot, Kafka, and gRPC, has given me a deep appreciation for the importance of scalable, reliable, and efficient applications. I have also had the opportunity to work on various projects, including an AI Resume Analyzer using Python, FastAPI, and Transformers, and a Medical Image Classifier using Python, TensorFlow, and CNN, which has further solidified my understanding of machine learning principles and their applications.

    I am excited about the prospect of joining NeuroGrid Technologies and contributing my skills and experience to the development of cutting-edge machine learning solutions. I am impressed by the company's commitment to innovation, collaboration, and continuous learning, and I am confident that my passion, work ethic, and dedication would make me a valuable asset to the team. I look forward to the opportunity to discuss my application and how I can contribute to the success of NeuroGrid Technologies.

    Thank you for considering my application. I am eager to bring my skills and experience to NeuroGrid Technologies and contribute to the development of innovative machine learning solutions.

    Sincerely,\\[12pt]

    Mahdi Jellali

\end{document}