```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge \scshape Mahdi Jellali} \\ \vspace{1pt}
\small
\faPhone\ +21655402817 \quad
\faEnvelope\ \href{mailto:mahdijellali2001@gmail.com}{mahdijellali2001@gmail.com} \quad
\href{https://github.com/mahdiJ2001}{GitHub} \quad
\href{https://concise-code-display.vercel.app/}{Portfolio} \quad
\href{https://www.linkedin.com/in/mahdi-jellali/}{LinkedIn}
\end{center}

\vspace{10pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National School of Engineers of Tunis (ENIT)}
{2021–2025}
{Bachelor’s in Software Engineering}
{}
\resumeSubheading
{Preparatory Institute for Engineering Studies of Sousse (IPEIS)}
{2019–2021}
{Preparatory Cycle in Mathematics and Physics}
{}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Wevioo}
{2024}
{Backend Developer Intern}
{Contributed to a microservices-based patient management system using \textbf{Spring Boot}, \textbf{Kafka}, and \textbf{gRPC}. Improved backend performance by implementing asynchronous event handling and optimizing serialization.}
\resumeSubheading
{TechLabs Tunisia}
{2023}
{Software Engineering Intern}
{Developed RESTful APIs in \textbf{Java} for data synchronization between legacy and cloud systems. Improved response times by \textbf{30\%} through query optimization.}
\resumeSubheading
{SmartIoT Solutions}
{2022}
{IoT Developer Intern}
{Built firmware for environmental sensors using \textbf{C++} and integrated real-time data streaming to \textbf{AWS IoT Core} with a monitoring dashboard.}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{Smart Home Energy Monitor — \textbf{C++}, \textbf{Arduino}, \textbf{MQTT}, \textbf{AWS IoT}: Built a smart energy monitoring system that collects power usage data and uploads it to AWS IoT for visualization.}
\resumeItem{AI Resume Analyzer — \textbf{Python}, \textbf{FastAPI}, \textbf{Transformers}, \textbf{OpenAI API}: Created an AI resume analyzer that evaluates and matches resumes to job descriptions using NLP.}
\resumeItem{Cloud Data Pipeline — \textbf{Python}, \textbf{Apache Airflow}, \textbf{AWS S3}, \textbf{Redshift}: Designed an ETL pipeline for large-scale financial data aggregation and transformation.}
\resumeItem{Medical Image Classifier — \textbf{Python}, \textbf{TensorFlow}, \textbf{CNN}: Built a CNN to detect lung diseases from X-rays with \textbf{92\% accuracy}, deployed with Flask.}
\resumeItem{Dynamic Financial Statement Platform — \textbf{Java}, \textbf{Spring Boot}, \textbf{Angular}, \textbf{PostgreSQL}: Web platform for creating and validating dynamic financial statements with DMN rule evaluation.}
\resumeItem{Distributed Log Processing System — \textbf{Go}, \textbf{Kafka}, \textbf{Docker}: Implemented a real-time distributed system for log analytics using Kafka streams.}
\resumeItem{Student Housing Rental App — \textbf{Spring Boot}, \textbf{Angular}, \textbf{MySQL}: Student housing platform allowing users to post, filter, and manage rental listings.}
\resumeItem{Quant Simulation Engine — \textbf{C++}, \textbf{ZeroMQ}, \textbf{Redis}: Built a high-performance trading simulation engine for algorithmic backtesting.}
\resumeItem{Real-Time Chat Application — \textbf{Node.js}, \textbf{Express}, \textbf{Socket.io}, \textbf{MongoDB}: Developed a live chat platform with WebSocket communication and persistent storage.}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Java}, \textbf{Spring Boot}, \textbf{Python}, \textbf{FastAPI}, \textbf{C++}, \textbf{Kafka}, \textbf{Docker}, \textbf{PostgreSQL}, \textbf{Angular}, \textbf{React}, \textbf{TensorFlow}, \textbf{AWS}, \textbf{Redis}, \textbf{gRPC}, \textbf{Go}, \textbf{Git}, \textbf{CI/CD}, \textbf{REST APIs}, \textbf{Data Structures}, \textbf{Algorithms}, \textbf{Microservices Architecture}
}}
\end{itemize}

\end{document}
```